---
title: "HW5 notebook"
output: html_notebook
---

Here is the first method for overlaying shape data on a raster.

Use the following packages (install them first), then use them via
the library() call: tmap, tmaptools, rgdal, sp, OpenStreetMap, osmdata

These calls are useful: readOGR(), tmaptools::read_osm(),
tm_shape(), tm_raster(), tm_dots()

1. readOGR() your shapefile, store it in a var
2. read_osm() the bbox of #1 above, store it in a var
3. do tm_shape() on #2 + tm_raster() +
tm_shape() on #1 + tm_dots() to specify point color and size

First I install the necessary packeges and load them.
I set my working directory to be where mygeodata file is saved.
```{r}
setwd("C:/Users/gelia/Documents/R")
install.packages("tmap")
install.packages("tmaptools")
install.packages("rgdal")
install.packages("sp")
install.packages("OpenStreetMap")
install.packages("osmdata")

library(tmap)
library(tmaptools)
library(rgdal)
library(sp)
library(OpenStreetMap)
library(osmdata)

```


I read the .shp file after converting my kml file from homework3.

I use red color and size 6 to match the example provided the HW page.

```{r}

shape <- readOGR("C:/Users/gelia/Documents/R/mygeodata" ,"hw5")
shape2 <- tmaptools::read_osm(shape)
tm_shape(shape2) + tm_raster() + tm_shape(shape) + tm_dots(col = "red",size = 6)

```


And here's the second.

Use these packages: PBSmapping, ggmap
And these calls: importShapefile(), as.data.frame(), get_map(), ggmap(), 
geom_point()

1. importShapefile() into a var
2. convert it (#1 above) to a dataframe, store it in a var
3. get_map() with a location that's in your collection of (lat,long),
store it in a var
4. do ggmap() on #3, + geom_point() on #2

Frist I will install the necessary packages and load them.
```{r}

install.packages("PBSmapping")
install.packages("ggmap")
library(PBSmapping)
library(ggmap)

```

The C:/Users/gelia/Documents/R/mygeodata is where my .shp file is and where all the files are saved after the conversion from kml using the website provided.

I set my working directory where my file is saved so I can import it using importShapeFile().

The files in the folder mygeodata have name hw5, that's why I used fn=hw5(filename = hw5).
I used as my location Tommy Trojan, in other word the most 'central' point on the map.
I chose it so that as many points as possible would be visible on the map.

I used zoom = 16 so that it would match what was shown in the example provided in the HW page. Still, not all points are visible on my map (1 point not visible).
That's why I get the warning - Removed 1 rows containing missing values.

```{r}

setwd("C:/Users/gelia/Documents/R/mygeodata")
myShape <- importShapefile(fn = 'hw5')
myShape2 <- as.data.frame(myShape)
location <- get_map(location = c(long = -118.2854 , lat = 34.02056), zoom = 16)
ggmap(location) + geom_point(data = myShape2 ,aes(x = X, y = Y),col = 'orange',size = 3)

```

